English-Chinese Translation Machine Based on Sequence to Sequence Network

### 2022-12-05 ML2/paper.tex
12-5

Training loss in this experience was a little discrepancy in between difference of maximum number of tokens in a sentence. For example, we attach two pictures which reflect the change of loss value in two different maximum number of tokens in a sentence like Fig.\ref{fig:loss1} with maximum of 20 while Fig.\ref{fig:loss2} with maximum of 15 in this experience.

@@

>>>>

Training loss in this experience was a little discrepancy in between difference of maximum number of tokens in a sentence. For example, we attach two pictures which reflect the change of loss value in two different maximum number of tokens in a sentence like Fig.\ref{fig:loss1} with maximum of 20 while Fig.\ref{fig:loss2} with maximum of 15 in this experience. This result shows that this model can fill all the sentences with max length of 15 and sentences with max length of 20.

In Fig.\ref{fig:result1}, we put a sentence with tokens as \textit{I am happy $ <EOS> $}. It shows these tokens relationship with some tokens in Chinese. Every tokens was been calculated an attention coefficient to other tokens. A lighter litter between two tokens means they have more tenacious relationship of themselves. In Fig.\ref{fig:result1}, it shows the relationship of all tokens in this sentence.

@@

 In this experience, we trained a model to translate sentence into another language. But in result of this experience, BLEU score of this model always be 1. We supposed this phenomenon signified this model just translated all the sentences from training dataset.
